Inferring Graphics Programs from Images

### 2017-05-17 paper.tex
added figures
better figures for synthetic results

Figure~\ref{syntheticResults}
compares the neural network with SMC against the neural network by
itself or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 8$
objects, it successfully parses scenes with many more objects than the
training data.
\begin{wrapfigure}{R}{0.5\textwidth}
  \begin{center}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-25-4.png}}\end{minipage}
%    \begin{minipage}[t]{2cm}\includegraphics[width=2cm]{figures/randomScene-26-7.png}\end{minipage}
%    \begin{minipage}[t]{2cm}\includegraphics[width=2cm]{figures/randomScene-19-3.png}\end{minipage}
  \end{center}
  \caption{Network is trained to infer execution traces for figures like the three shown above.}\label{trainingData}
\end{wrapfigure}

\begin{figure}
  \begin{minipage}[t]{15cm}
    \includegraphics[width = 15cm]{figures/editDistance.png}
  \end{minipage}\\
  \begin{minipage}[t]{15cm}
    \includegraphics[width = 15cm]{figures/accuracy.png}
  \end{minipage}\\
  \begin{minipage}[t]{15cm}
    \includegraphics[width = 15cm]{figures/time.png}
  \end{minipage}
  \caption{Using the model to parse latex output. The model is trained on diagrams with up to 8 objects. As shown above it generalizes to scenes with many more objects. Neither the stochastic search nor the neural network are sufficient on their own.}\label{syntheticResults}
\end{figure}

\subsection{Generalizing to hand drawings}
A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We train the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (figure~\ref{handDrawingExamples}).
Our neurally-guided SMC procedure
used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in section~\ref{neuralNetworkSection}).
But pixel-wise distance fares poorly on hand drawings, which never exactly match
the model's renders.
So, for hand drawings,
we \emph{learned} a surrogate likelihood function.
Our learned $L(\cdot|\cdot)$
is a convolutional network that we train to predict
the distance between two traces conditioned upon their renderings.
Formally we train our likelihood surrogate to approximate:
\begin{equation}
  L(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
  \end{equation}

@@

Why synthesize a graphics program,
if the execution trace already suffices to recover the objects in an image?
Within our domain of hand-drawn figures, graphics program synthesis has several uses:
\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
For example,
we can change all of the circles to squares,
were make all of the lines be dashed.
We can also \textbf{extrapolate} figures
by increasing the number of times that loops are executed.
%\input{extrapolations.tex}

>>>>

Figure~\ref{syntheticResults}
compares the neural network with SMC against the neural network by
itself or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 8$
objects, it successfully parses scenes with many more objects than the
training data.

\begin{figure}\centering
  \begin{minipage}{0.35\textwidth}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
    \caption{Network is trained to infer execution traces for randomly generated figures like the two shown above.}\label{trainingData}
  \end{minipage}\hfill
  \begin{minipage}{0.6\textwidth}
    \includegraphics[width = 4cm]{figures/editDistance.png}
    \includegraphics[width = 4cm]{figures/accuracy.png}
      \caption{Using the model to parse latex output. The model is trained on diagrams with up to 8 objects. As shown above it generalizes to scenes with many more objects. Neither the stochastic search nor the neural network are sufficient on their own.}\label{syntheticResults}
    \end{minipage}

  \end{figure}

\subsection{Generalizing to hand drawings}
A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
 We train the model
to generalize to hand drawings by introducing noise into the
renderings of the training target images.
We designed this noise process to introduce the kinds of variations found in hand drawings (figure~\ref{handDrawingExamples}).
Our neurally-guided SMC procedure
used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in section~\ref{neuralNetworkSection}).
But pixel-wise distance fares poorly on hand drawings, which never exactly match
the model's renders.
So, for hand drawings,
we \emph{learned} a surrogate likelihood function.
Our learned $L(\cdot|\cdot)$
is a convolutional network that we train to predict
the distance between two traces conditioned upon their renderings.
Formally we train our likelihood surrogate to approximate:
\begin{equation}
-\log L(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
  \end{equation}

@@

Why synthesize a graphics program,
if the execution trace already suffices to recover the objects in an image?
Within our domain of hand-drawn figures, graphics program synthesis has several uses:
\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
For example,
we can change all of the circles to squares,
were make all of the lines be dashed.
We can also \textbf{extrapolate} figures
by increasing the number of times that loops are executed.

\includegraphics[width = 8in]{figures/extrapolationMatrix.png}
%\input{extrapolations.tex}
